---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(rnwb.max_lines = 10)
```

# rnwb

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `rnwb` is to provide R users access to ["Neurodata Without Borders" (NWB)](https://www.nwb.org/). This access is viable through the NWB official Python package [pynwb](https://github.com/NeurodataWithoutBorders/pynwb) and Python-to-R tunnel provided by [RAVE (Reproducible framework for Analyzing and Visualizing intracranial EEG)](https://rave.wiki)

## Installation

The package is not on CRAN (yet). You can install the development version of `rnwb` like so:

``` r
## First, install R package
# install.packages("remotes")
remotes::install_github("dipterix/rnwb")

## Next, set up environment (one-time code)
rnwb::install_nwb()
```

## Example

This is a basic example of reading a `NWB` file:

```{r kickstart, eval = FALSE}
file <- "<path to .nwb>"
# Open a NWB file proxy
proxy <- rnwb::NWBHDF5IO$new(file, mode = "r")

# Use `with` to properly close the files at the end
proxy$with({
  nwb_data <- proxy$read()
  electrodes <- nwb_data$electrodes
  
  columns_to_extract <- c("location", "filtering", "channID", "hemisph", "label")
  
  # Use `[]` to load data into memory
  # Use `convert = TRUE` to convert table to an R object
  electrode_table <- electrodes[ , columns_to_extract, convert = TRUE]
})

# Pretty-print
data.table::data.table(electrode_table)
#>                 location filtering channID hemisph       label
#>   1:            amygdala  300-3000     257       L  MI_D1_C257
#>   2:            amygdala  300-3000     258       L  MI_D1_C258
#>   3:            amygdala  300-3000     259       L  MI_D1_C259
#>   4:            amygdala  300-3000     260       L  MI_D1_C260
#>   5:            amygdala  300-3000     261       L  MI_D1_C261
#>  ---                                                          
#> 166: posterior cingulate  0.1-1000     150       R MA_D13_C150
#> 167: posterior cingulate  0.1-1000     151       R MA_D13_C151
#> 168: posterior cingulate  0.1-1000     152       R MA_D13_C152
#> 169: posterior cingulate  0.1-1000     153       R MA_D13_C153
#> 170: posterior cingulate  0.1-1000     154       R MA_D13_C154
```

You can also access the low-level Python code via R:

```{r simplecase}
nwb <- rnwb::load_nwb()
print(nwb)

# Get elements/functions in R via `$`
nwb$NWBFile
```

